The evolution of the transcriptome of mammalian placentas

### 2016-11-14 manuscript/manuscript.Rnw
switch to acro from acronym
use bw/gene expression in core plot

%\documentclass[english,12pt]{article}
\documentclass[5p]{elsarticle_dla}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\setmathrm{FreeSerif}
\setmathsf{FreeSans}
\setmathtt{FreeSerif}
%\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
%\usepackage[letterpaper]{geometry}
%\usepackage{url}
\usepackage{graphicx}
%\usepackage{rotating}
%\usepackage{wrapfig}
\usepackage{booktabs}
%\usepackage{float}
\usepackage{multirow}
%\usepackage{setspace}
\usepackage{acronym}
\usepackage{array}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=black,citecolor=blue,breaklinks=true]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads]{endfloat}
% \renewcommand{\efloatseparator}{\mbox{}}
%\AtBeginFigures{\newpage \renewcommand{\efloatseparator}{\mbox{}}\section*{Figure Legends}}
%\AtBeginTables{\newpage \section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
% \renewcommand{\includegraphics}[2][]{}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\newcommand{\DEW}[1]{\textcolor{purple}{\fxnote{DEW: #1}}}
% \usepackage[x11names,svgnames]{xcolor}
% \usepackage{texshade}
% \usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
% this package will stretch the font slightly if necessary.
% \usepackage{microtype}
\usepackage{zref-xr,zref-user}
\zxrsetup{toltxlabel}
\zexternaldocument*{supplemental_material}
\usepackage[capitalize]{cleveref}
\def\UrlBreaks{\do\.\do\@\do\\\do\/\do\!\do\_\do\|\do\;\do\>\do\]%
\do\)\do\,\do\?\do\&\do\'\do+\do\=\do\#%
\do\/%
}%
\input{common_latex}
\tolerance=5000
\emergencystretch=0.1pt

@@

print(ggplot(cptl,aes(x=human_name,y=FPKM))+
      geom_boxplot(outlier.shape=NA)+
      scale_y_log10(labels=trans_format("log10", math_format(10^.x)))+
      geom_point(aes(color=Species,shape=Species))+
      scale_shape_manual("Species",
                         guide=guide_legend(#nrow=1,
                                            keywidth=unit(3,"mm"),
                                            keyheight=unit(3,"mm"),
                                            label.theme=element_text(face="italic",
                                                                     angle=0,
                                                                     size=9),
                                            title.position="top"
                                            ),
                         values=0:18)+
      # scale_color_discrete(NULL)+
      coord_flip()+
      xlab("Human Ortholog Name")+
      ylab("FPKM")+
      theme(legend.position=c(0.7,0.15),
            axis.text.y=element_text(face="italic"),
            legend.margin=unit(0,"mm"),
            legend.justification="left",
            plot.margin=unit(c(0,0,0,0),"mm")
            ))
@ 
\caption{Core Placenta Transcriptome.
  \Sexpr{core.placenta.transcriptome.long[,length(unique(human_name))]}
  1:1 \human ortholog genes expressed (\ac{FPKM}$ \ge 10$) in the
  placenta of all \Sexpr{star.logs[,length(unique(species))]} species
  studied with housekeeping genes
  \cite{Eisenberg.ea2013:Humanhousekeepinggenesrevisited} removed
  ordered (from top to bottom) by median expression. Supplemental
  \cref{fig:core_placenta_transcriptome_shape} shows the shape of the
  distribution of the number of genes in the core placenta
  transcriptome if different FPKM and species restriction criteria are
  utilized.}
\label{fig:core_placenta_transcriptome}
\end{figure}

>>>>

%\documentclass[english,12pt]{article}
\documentclass[5p]{elsarticle_dla}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\setmathrm{FreeSerif}
\setmathsf{FreeSans}
\setmathtt{FreeSerif}
%\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
%\usepackage[letterpaper]{geometry}
%\usepackage{url}
\usepackage{graphicx}
%\usepackage{rotating}
%\usepackage{wrapfig}
\usepackage{booktabs}
%\usepackage{float}
\usepackage{multirow}
%\usepackage{setspace}
\usepackage{acro}
\usepackage{array}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=black,citecolor=blue,breaklinks=true]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads]{endfloat}
% \renewcommand{\efloatseparator}{\mbox{}}
%\AtBeginFigures{\newpage \renewcommand{\efloatseparator}{\mbox{}}\section*{Figure Legends}}
%\AtBeginTables{\newpage \section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
% \renewcommand{\includegraphics}[2][]{}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\newcommand{\DEW}[1]{\textcolor{purple}{\fxnote{DEW: #1}}}
% \usepackage[x11names,svgnames]{xcolor}
% \usepackage{texshade}
% \usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
% this package will stretch the font slightly if necessary.
% \usepackage{microtype}
\usepackage{zref-xr,zref-user}
\zxrsetup{toltxlabel}
\zexternaldocument*{supplemental_material}
\usepackage[capitalize]{cleveref}
\def\UrlBreaks{\do\.\do\@\do\\\do\/\do\!\do\_\do\|\do\;\do\>\do\]%
\do\)\do\,\do\?\do\&\do\'\do+\do\=\do\#%
\do\/%
}%
\input{common_latex}
\tolerance=5000
\emergencystretch=0.1pt

@@

print(ggplot(cptl,aes(x=human_name,y=FPKM))+
      geom_boxplot(outlier.shape=NA)+
      scale_y_log10(labels=trans_format("log10", math_format(10^.x)))+
      geom_point(aes(color=Species,shape=Species))+
      scale_shape_manual("Species",
                         guide=guide_legend(#nrow=1,
                                            keywidth=unit(3,"mm"),
                                            keyheight=unit(3,"mm"),
                                            label.theme=element_text(face="italic",
                                                                     angle=0,
                                                                     size=9),
                                            title.position="top"
                                            ),
                         values=0:18)+
      # scale_color_discrete(NULL)+
      coord_flip()+
      xlab("Human Ortholog Name")+
      ylab("Gene Expression (FPKM)")+
      theme_bw() +
      theme(legend.position=c(0.7,0.15),
            axis.text.y=element_text(face="italic"),
            legend.margin=unit(0,"mm"),
            legend.justification="left",
            plot.margin=unit(c(0,0,0,0),"mm")
            ))
@ 
\caption{Core Placenta Transcriptome.
  \Sexpr{core.placenta.transcriptome.long[,length(unique(human_name))]}
  1:1 \human ortholog genes expressed (\ac{FPKM}$ \ge 10$) in the
  placenta of all \Sexpr{star.logs[,length(unique(species))]} species
  studied with housekeeping genes
  \cite{Eisenberg.ea2013:Humanhousekeepinggenesrevisited} removed
  ordered (from top to bottom) by median expression. Supplemental
  \cref{fig:core_placenta_transcriptome_shape} shows the shape of the
  distribution of the number of genes in the core placenta
  transcriptome if different FPKM and species restriction criteria are
  utilized.}
\label{fig:core_placenta_transcriptome}
\end{figure}
